Data Predictive Control with Random Forests:\\Theory and Applications\tnoteref{mytitlenote}

### 2017-09-27 paper/intro.tex
Couple of small changes in abstract, intro and keywords

\subsection{Main contributions and paper organization}
In our previous work \cite{Behl2016,Jain2016,JainACC2017,JainCDC2017}, we introduced the concept of DPC for receding horizon control. In this paper, we extend these results providing the following contributions:
\begin{enumerate}
	\item In Section \ref{S:dpc}, we formally present the two following control techniques:
	\begin{itemize}
		\item DPC with regression trees, and
		\item DPC with random forests.
	\end{itemize}
	\item In Section \ref{S:proof}, we demonstrate the strength of DPC for receding horizon control via one-to-one comparison against a benchmark MPC controller using a bilinear building model whose parameters were identified using experiments on a building in Switzerland. We show that DPC captures 70\% variance in MPC and offers a comparable performance.
	\item Section \ref{S:casestudy} describes a practical application of DPC for Demand Response, where we apply DPC to a 6 story 22 zone building model in EnergyPlus \cite{Crawley2001} for which model-based control is not economical and practical due to extreme complexity. We show scalability and efficiency of DPC in providing financial incentives to the end-customers bypassing the need for high fidelity models. We observe that DPC provides the desired power reduction with an average error of 3\%.
	\item In Section \ref{S:realCaseStudy}, we implement DPC on the real data from an off-grid house located in L'Aquila (Italy), to find the optimal ON/OFF scheduling for the heating system in order to save energy while guaranteeing thermal comfort for the occupants. We quantify the total amount of energy saved, with respect to the classical bang-bang controller widely used in houses for temperature control, using an EnergyPlus model built specifically for the house. We show we can perform an energy saving that goes from $25\%$, if we guarantee thermal comfort, to $50\%$, if we allow very little discomfort in terms of rooms' temperature.
\end{enumerate}

>>>>

\subsection{Main contributions and paper organization}
In our previous work \cite{Behl2016,Jain2016,JainACC2017,JainCDC2017}, we introduced the concept of DPC for receding horizon control. In this paper, we extend these results providing the following contributions:
\begin{enumerate}
	\item In Section \ref{S:dpc}, we formally present the two following control techniques:
	\begin{itemize}
		\item DPC with regression trees, and
		\item DPC with random forests.
	\end{itemize}
	\item In Section \ref{S:proof}, we demonstrate the strength of DPC for receding horizon control via one-to-one comparison against a benchmark MPC controller using a bilinear building model whose parameters were identified using experiments on a building in Switzerland. We show that DPC captures 70\% variance in MPC and offers a comparable performance.
	\item Section \ref{S:casestudy} describes a practical application of DPC for Demand Response, where we apply DPC to a 6 story 22 zone building model in EnergyPlus \cite{Crawley2001} for which model-based control is not economical and practical due to extreme complexity. We show scalability and efficiency of DPC in providing financial incentives to the end-customers bypassing the need for high fidelity models. We observe that DPC provides the desired power reduction with an average error of 3\%.
	\item In Section \ref{S:realCaseStudy}, we implement DPC on the real data from an off-grid house located in L'Aquila (Italy), to find the optimal ON/OFF scheduling for the heating system in order to save energy while guaranteeing thermal comfort for the occupants. We quantify the total amount of energy saved, with respect to the classical bang-bang controller widely used in houses for temperature control, using an EnergyPlus model built specifically for the house. We show we can perform an energy saving that goes from $25.4\%$, if we guarantee thermal comfort, to $49.2\%$, if we allow very little discomfort in terms of rooms' temperature.
\end{enumerate}
